Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-16 main.Rmd
A recommendation of appropriate distribution displays is provided  - deleted from abstract
Antony's comments on§5.3 addressed

 Time granularities can be used to create data visualizations to explore for periodicities, associations and anomalies. The granularities form categorical variables (ordered or unordered) which induce groupings of the observations. Assuming a numeric response variable, the resulting graphics are then displays of distributions compared across combinations of categorical variables. A recommendation of appropriate distribution displays is provided.

@@

- Data: <$C_i$, $C_j$, $v$>;
- Aesthetic mapping (mapping of variables to elements of the plot): $C_i$ mapped to $x$ position and $v$ to $y$ position;
- Facet (split plots): $C_j$;
- Statistical transformation (data summarization): any descriptive or smoothing statistics that summarizes the distribution of $v$;
- Geometric objects (physical representation of the data): any geometry displaying the distribution; for example, boxplot, letter value, violin, ridge or highest density region plots.

## Choice of statistical transformations and geometric objects

@@

>>>>

 Time granularities can be used to create data visualizations to explore for periodicities, associations and anomalies. The granularities form categorical variables (ordered or unordered) which induce groupings of the observations. Assuming a numeric response variable, the resulting graphics are then displays of distributions compared across combinations of categorical variables.

@@

- Data: <$C_i$, $C_j$, $v$>;
- Aesthetic mapping (mapping of variables to elements of the plot): $C_i$ mapped to $x$ position and $v$ to $y$ position;
- Facet (split plots): $C_j$;
- Data summarization: any descriptive or smoothing statistics that summarizes the distribution of $v$;
- Geometric objects (physical representation of the data): any geometry displaying the distribution; for example, boxplot, letter value, violin, ridge or highest density region plots.

## Data summarization and geometric objects

@@

\noindent Visualizing distributions can be uninformative or potentially misleading if data summarization are performed on rarely occurring categories (Section&nbsp;\ref{sec:near-clashes}). Even when there are no rarely occurring events, the number of observations may vary greatly within or across each facet, due to missing observations or uneven locations of events in the time domain. In such cases, data summarization should be used with caution as sample sizes will directly affect the accuracy of the estimated quantities being displayed.
